Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex
Combined SUP and CUP results into the same figure and discussion.

\subsection{Neutron fluence rate, spatial distribution and spectrum}
Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
The collimation effect is clearly visible.
Fig.~\ref{fig:SUPProfile} shows neutron fluence profile at the SUP.
In Fig.~\ref{fig:SUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating measurement with a \U238\ TFBC~\cite{Prokofiev2009}.

Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
The parameterisation therefore exceeds the current calculations by 31\%.

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{SUP10ColSpatialDistribution10MeVRADECS.png}
    \caption{
        Spatial distribution of neutrons above \SI{10}{\MeV} at the SUP.
        Concentric white circles indicate nominal umbra and penumbra limits.
    }
    \label{fig:SUPDensity}
\end{figure}

>>>>

\subsection{Neutron fluence rate, spatial distribution and spectrum}
Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
The collimation effect is clearly visible.
Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofiev2009}.
The parameterisation therefore exceeds the present calculations by 31\%.

\begin{figure}[t]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{SUP10ColSpatialDistribution10MeVRADECS.png}
        \subcaption{
            Standard User Position.
            Concentric white circles indicate nominal umbra and penumbra limits.
        }
        \label{fig:SUPDensity}
    \end{minipage}
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\columnwidth]{CUP10ColSpatialDistribution10MeV.png}
        \subcaption{Close User Position}
        \label{fig:CUPDensity}
    \end{minipage}
    \caption{
        Spatial distribution of neutrons above \SI{10}{\MeV} at SUP and CUP.
        \SI{10.2}{\cm} diameter collimator.
    }
    \label{fig:SUPDensity}
\end{figure}

Fig.~\ref{fig:CUPDensity} shows equivalent data for the CUP.
The results show\ldots
\todo{Describe the results: contours and profile at CUP}
In the central region the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from the standard facility parameterisation~\cite{Prokofie14}.
The parameterisation therefore exceeds the present calculations about TBD\%.
\todo{Complete quantification at CUP}.

Fig.~\ref{fig:SUPProfile} shows neutron fluence profile at the SUP.
In Fig.~\ref{fig:SUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating measurement with a \U238\ TFBC~\cite{Prokofiev2009}.
